What We Eval in the Shadows

### 2021-08-09 paper/main.tex
Update S4

\paragraph{Summary}

\Eval is used in CRAN packages. Nearly every fourth package contains at least
one \eval site. However, most packages that use \eval do that modestly. Half of
them contain less than three \eval sites. Packages that rely heavily on \eval
are mostly the ones that provide functions for statistical modeling and
simulation. At runtime, over third of extracted programs triggered calls to
\eval. Half of the \packageAllcallsRnd recorded calls come from a single \eval
site, but for the rest, most of the packages have low \eval call frequency.

>>>>

\paragraph{Discussion}

\Eval is used in CRAN packages. Nearly every fourth package contains at least
one \eval site. However, most packages that use \eval do that modestly. Half of
them include less than three \eval sites. Packages that rely heavily on \eval
are mostly the ones that provide statistical modeling and simulation functions.
At runtime, over a third of extracted programs triggered calls to \eval. Half
of the \packageAllcallsRnd recorded calls come from a single \eval site, but
for the rest, most of the packages have low \eval call frequency.
